Usability of Mobile Map Applications

### 2014-09-25 usability-study/usability-study.tex
conclusion work

The usability metrics of the Google Maps mobile application outranked those of the Apple Maps application in almost every way. Though there are some problems with the UI consistency, it does not seem to bother the users (refer back to satisfaction). Still, using non-standard icons or processes isn't without drawbacks. It's loud. It's authorial voice. It's greater cognitive load for users. Anything inconsistent, first or third party is. On an integrated platform like iOS, integrating with the platform offers a lot of benefits, especially when it comes to user experience.

If you use Google apps, either a lot or a little, does the lack of iOS-style buttons make any difference to you?

must recognize that there are limitations to our studies-- didn't test all five metrics; less data for Apple maps; Apple maps is newer; etc.
Judgment call -- google maps with data that we have now.
\clearpage
\begin{thebibliography}{100} % 100 is a random guess of the total number of 
%references
\bibitem{Nielsen} Nielsen, Jakob, \emph{Usability Engineering}, Boston: Academic, 1993.
\bibitem{Mossberg} Mossberg, Walt., ``The iPhone Takes to the Big Screen," \emph{The Wall Street Journal}, September 2012.
\bibitem{ComScore}``Analytics for a Digital World - ComScore, Inc." \emph{ComScore, Inc}, 2012.
\bibitem{Fitts}Fitts, Paul M. ``The information capacity of the human motor system in controlling the amplitude of movement" \emph{Journal of Experimental Psychology}, June 1954.
\bibitem{Google} \emph{Material Design}, www.google.com/design/spec/material-design.
\bibitem{Apple} \emph{iOS Human Interface Guidelines}, https://developer.apple.com/
\end{thebibliography}
%%%%%%%%%%%%% end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

The usability metrics of the Google Maps mobile application outranked those of the Apple Maps application in almost every way. Though there are some inconsistencies with the user interface (UI) of the Google Maps mobile app that are not present in the UI of the Apple Maps mobile app, the users were still more satisfied in general with Google Maps. 
My heuristic evaluation for Google Maps focuses on the app's decision to not use standard iOS icons. One must recognize that using non-standard icons or processes isn't without drawbacks. It's loud. It's authorial voice. It's greater cognitive load for users. Anything inconsistent, first or third party is. On an integrated platform like iOS, integrating with the platform offers a lot of benefits, especially when it comes to user experience.

must recognize that there are limitations to our studies-- didn't test all five metrics; less data for Apple maps; Apple maps is newer; etc.
Judgment call -- google maps with data that we have now.
\clearpage
\begin{thebibliography}{100} % 100 is a random guess of the total number of 
%references
\bibitem{Apple} \emph{iOS Human Interface Guidelines}, https://developer.apple.com.
\bibitem{ComScore}``Analytics for a Digital World - ComScore, Inc." \emph{ComScore, Inc}, 2012.
\bibitem{Fitts}Fitts, Paul M. ``The information capacity of the human motor system in controlling the amplitude of movement" \emph{Journal of Experimental Psychology}, June 1954.
\bibitem{Google} \emph{Material Design}, www.google.com/design/spec/material-design.
\bibitem{Mossberg} Mossberg, Walt., ``The iPhone Takes to the Big Screen," \emph{The Wall Street Journal}, September 2012.
\bibitem{Nielsen} Nielsen, Jakob, \emph{Usability Engineering}, Boston: Academic, 1993.
\end{thebibliography}
%%%%%%%%%%%%% end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
